Combine filtered data from all three studies in AMP-AD for metanalysis

### 2017-05-08 code/Rmd/combineAllRNASeqData.Rmd
Added markdown to perform differential expression analysis in every brain region

# Modify ROSMAP covariates
rosmap.key = downloadFile('syn3382527') %>%
  dplyr::select(projid, mrna_id) %>%
  tidyr::separate(mrna_id, c('a','b','c'), sep = '_') %>%
  tidyr::unite(SampleID, a,b, sep = '_') %>%
  dplyr::rename(Donor_ID = projid)
all.used.ids = c(all.used.ids, 'syn3382527')

covariates$ROSMAP = covariates$ROSMAP %>%
  left_join(rosmap.key) %>%
  dplyr::mutate(Gender = factor(msex, levels = c(0,1), labels = c('0' = 'FEMALE', '1' = 'MALE')),
                RIN = RINcontinuous,
                AAD = age_death,
                PMI = pmi,
                BrainRegion = 'DLPFC',
                Study = 'ROSMAP') %>%
  dplyr::select(SampleID, Donor_ID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

>>>>

# Modify ROSMAP covariates
rosmap.donorinfo <- downloadFile('syn4300313') %>%
  dplyr::rename(SampleID = Sampleid, Donor_ID = projid) %>%
  dplyr::select(SampleID, Donor_ID) %>%
  unique %>%
  dplyr::filter(!(SampleID == '492_120515' & is.na(Donor_ID)))
all.used.ids = c(all.used.ids, 'syn4300313')

covariates$ROSMAP = covariates$ROSMAP %>%
  left_join(rosmap.donorinfo) %>%
  dplyr::mutate(Gender = factor(msex, levels = c(0,1), labels = c('0' = 'FEMALE', '1' = 'MALE')),
                RIN = RINcontinuous,
                AAD = age_death,
                PMI = pmi,
                BrainRegion = 'DLPFC',
                Study = 'ROSMAP') %>%
  dplyr::select(SampleID, Donor_ID, Study, BrainRegion, Diagnosis, Batch, Gender, RIN, AAD, PMI, PCT_PF_READS_ALIGNED,
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES) 
covariates$ROSMAP$Donor_ID[is.na(covariates$ROSMAP$Donor_ID)] = paste0('NotAva',1:sum(is.na(covariates$ROSMAP$Donor_ID)))
